A New Hybrid Machine Learning Method for Stellar Parameter Inference

### 2025-03-05 paper/paper2/paper.tex
Fix references running off page

Finally, the state dictionary is fed into \texttt{blase}'s \texttt{SparseLinearEmulator}, which reconstructs the spectrum by constructing a forward model based on the input state dictionary.
Any \texttt{nan} values are set to 1 (which we can do because the spectra are all normalized), and the spectral reconstruction is complete.
\textbf{In \autoref{fig:figure5}, we see a comparison between a PHOENIX generator solar spectrum and two nearby native PHOENIX grid point spectra at the 10123.66 \AA \ He II spectral line.}
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figure5}
    \caption{Plot of \textbf{the 10123.66 \AA \ He II} spectral line shown at the closest PHOENIX grid points to the Sun's stellar parameters \textbf{(solid lines)}, as well as a solar spectrum reconstructed with the PHOENIX generator \textbf{(dotted line)}.}
    \label{fig:figure5}
\end{figure}

@@

\bibliography{paper}

>>>>

Finally, the state dictionary is fed into \texttt{blase}'s \texttt{SparseLinearEmulator}, which reconstructs the spectrum by constructing a forward model based on the input state dictionary.
Any \texttt{nan} values are set to 1 (which we can do because the spectra are all normalized), and the spectral reconstruction is complete.
\textbf{In \autoref{fig:figure5}, we see a comparison between a PHOENIX generator solar spectrum and two nearby native PHOENIX grid point spectra at the 10123.66 \AA \ He II spectral line.}
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figure5}
    \caption{Plot of \textbf{the 10123.66 \AA \ He II} spectral line shown at PHOENIX grid points \textbf{in the neighborhood of} the Sun's stellar parameters \textbf{(solid lines)}, as well as a \textbf{reconstruction at solar parameters} with the PHOENIX generator \textbf{(dotted line)}.}
    \label{fig:figure5}
\end{figure}

@@

\pagebreak
\bibliography{paper}
